Information carried by thalamocortical axons enables self-organization of the barrel field

### 2019-11-25 paper/briefpaper/brief.tex
Work on significance statement

% Please add a significance statement to explain the relevance of your work
\significancestatement{The mystacial whiskers of the rat are a complex,
  ordered set of structures whose pattern is repeated several times in
  separate locations in the brain. We contribute a mechanism by which their
  spatially ordered pattern can be recreated in a self-organising process
  which requires minimal genetic pre-determination.}

>>>>

% Please add a significance statement to explain the relevance of your work
\significancestatement{The mystacial whiskers of rodents are a complex,
  spatially ordered set of structures whose pattern is repeated in several
  locations in the brain. We contribute a self-organising mechanism by which
  the pattern can be recreated with minimal genetic pre-determination at each
  location; only two pairs of axon guidance gradients are required in each
  tissue. The pattern's togography is carried by the axons which grow from one
  tissue to another and interact variably (depending upon which whisker they
  are associated with) with the guidance gradients in the target tissue whilst
  competing with each other for space. We demonstrate that this mechanism
  recreates a realistic whisker barrel field and also accounts for the results
  of well-known gene misexpression experiments.}
